### 2017-01-15 sec-model.tex
Switch to JEDM theme for a EDM 2017 Journal Track submission.
Fix extraneous alignment character.
Address Cheng's comments.

\subsection{Formal Definition of TL-HMM}

@@

Thus, the probability of a sequence $\mathbf{s}$ of length $M$ given its
latent state $u$ is
\begin{equation}
  P(\mathbf{s} \mid \lambda^{(u)}) = P(a_1 \mid \pi^{(u)}) \prod_{i=2}^M P(a_i \mid
  a_{i-1}, A^{(u)})
\end{equation}
where $P(a \mid \pi^{(u)}) = \pi^{(u)}_a$ is the probability of starting
with action $a$ and $P(a_i \mid a_{i-1}, A^{(u)}) = A^{(u)}_{a_{i-1}, a_i}$
is the transition probability of moving from action $a_{i-1}$ to $a_{i}$.

We can compute the likelihood of a list of action sequences
$\mathbf{S}_\ell$ of length $N$ for a student $\ell$ by marginalizing over
all possible latent state sequences $U=(v_1, \ldots, v_N)$ as
\begin{equation}
  \begin{split}
  P(\mathbf{S}_\ell \mid \Lambda)
  &= \sum_U \left(P(v_1 \mid \Lambda) P(\mathbf{s}_1 \mid \lambda^{(v_1)})
  \phantom{\prod_{i=2}^N}\right.\\
  &\quad \left.\times \prod_{i=2}^N P(v_i \mid v_{i-1}, \Lambda)
  P(\mathbf{s}_i \mid \lambda^{(v_i)})\right)
  \end{split}
\end{equation}
where $\Lambda$ is the set of all model parameters.  In our model, we let
$\Lambda = (\pi, A, \lambda^{(1)}, \ldots, \lambda^{(K)})$ where $\pi$ and
$A$ are the parameters of a first-order Markov model over the latent states
and each $\lambda^{(i)}$ consists of the parameters for the first-order
Markov model over action sequences for latent state $i$. Thus $\pi$
(without superscripts) is an initial probability vector of length $K$ and
$A$ (without superscripts) is a $K \times K$ transition probability matrix,
analogous to the case with the individual first-order Markov model
parameters $\lambda^{(i)}$ for each latent state.

>>>>

\subsection{Formal Definition of the TL-HMM}

@@

Thus, the probability of a sequence $\mathbf{s}$ of length $M$ given its
latent state $u$ is
\begin{equation}
  P(\mathbf{s} \mid \lambda^{(u)}) = P(a_1 \mid \pi^{(u)}) \prod_{i=2}^M P(a_i \mid
  a_{i-1}, A^{(u)})
\end{equation}
where $P(a \mid \pi^{(u)}) = \pi^{(u)}_a$ is the probability of starting
with action $a$ and $P(a_i \mid a_{i-1}, A^{(u)}) = A^{(u)}_{a_{i-1}, a_i}$
is the transition probability of moving from action $a_{i-1}$ to $a_{i}$
given that the model is currently in latent state $u$.

We can compute the likelihood of a list of action sequences
$\mathbf{S}_\ell$ of length $N$ for a student $\ell$ by marginalizing over
all possible latent state sequences $(v_1, \ldots, v_N) \in U$ as
\begin{equation}
  P(\mathbf{S}_\ell \mid \Lambda)
  = \sum_{(v_1, \ldots, v_N) \in U} \left(P(v_1 \mid \Lambda)
  P(\mathbf{s}_1 \mid \lambda^{(v_1)}) \times \prod_{i=2}^N P(v_i \mid
  v_{i-1}, \Lambda) P(\mathbf{s}_i \mid \lambda^{(v_i)})\right)
\end{equation}
where $\Lambda$ is the set of all model parameters.  In our model, we let
$\Lambda = (\pi, A, \lambda^{(1)}, \ldots, \lambda^{(K)})$ where $\pi$ and
$A$ are the parameters of a first-order Markov model over the latent states
and each $\lambda^{(i)}$ consists of the parameters for the first-order
Markov model over action sequences for latent state $i$. Thus $\pi$
(without superscripts) is an initial probability vector of length $K$ and
$A$ (without superscripts) is a $K \times K$ transition probability matrix,
analogous to the case with the individual first-order Markov model
parameters $\lambda^{(i)}$ for each latent state.

### 2017-01-15 sec-results.tex
Address Cheng's comments.

\subsection{Latent State Representations}
First, we fit a 6-state TL-HMM to the \textretrieval{} sequence dataset and
show some of the latent state representations we find. We used the
following ten actions as our action set $\mathbf{A}$:
\begin{enumerate*}[label=(\arabic*)]
  \item quiz start,
  \item quiz submit,
  \item wiki (course material),
  \item forum list (view the list of all forums),
  \item forum thread list (view the list of all threads in a specific
    forum),
  \item forum thread view (view the list of posts within a specific
    thread),
  \item forum search (a search query issued against the forum),
  \item forum post thread (a new thread was posted),
  \item forum post reply (a new post was created within an existing
    thread), and
  \item view lecture (defined as either streaming or downloading a lecture
    video).
\end{enumerate*}

>>>>

\subsection{Latent State Representations}
The TL-HMM is meant to be a tool for exploratory analysis of student
behavior. As such, the number of states should be empirically set based on
the goal of analysis. A higher number of states will lead to a
finer-grained modeling of student behavior. In our experiments, we explored
using between 2--6 states. First, we fit a 6-state TL-HMM to the
\textretrieval{} sequence dataset and show some of the latent state
representations we find. We used the following ten actions as our action
set $\mathbf{A}$:
\begin{enumerate*}[label=(\arabic*)]
  \item quiz start,
  \item quiz submit,
  \item wiki (course material),
  \item forum list (view the list of all forums),
  \item forum thread list (view the list of all threads in a specific
    forum),
  \item forum thread view (view the list of posts within a specific
    thread),
  \item forum search (a search query issued against the forum),
  \item forum post thread (a new thread was posted),
  \item forum post reply (a new post was created within an existing
    thread), and
  \item view lecture (defined as either streaming or downloading a lecture
    video).
\end{enumerate*}
